An excess of positive results: Comparing the standard Psychology literature with Registered Reports

### 2022-03-10 preprint/positive_results_SRs_RRs.tex
updated disclaimer from "article is in press" to "article is published" (with DOI and all) and made very minor copy edits (e.g. added Mitchell's middle initials)

\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
% Manuscript styling
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Positive Results in Standard vs Registered Reports}
\author{Anne M. Scheel\textsuperscript{1}, Mitchell Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology}
\authornote{

@@

\abstract{
\vspace{0.4cm} \begin{tcolorbox}[colback=white,colframe=electricviolet,coltext=electricviolet,
   fontupper=\normalsize,borderline={0.3mm}{0.3mm}{white}]
 The present version of this manuscript has been accepted for publication at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
  \vspace{0.2cm}
 \begin{center}
 Scheel, A. M., Schijen, M., \& Lakens, D. (in press). An excess of positive results: Comparing the standard Psychology literature with Registered Reports. \textsl{Advances in Methods and Practices in Psychological Science}.
 \end{center}
\end{tcolorbox} \vspace{0.5cm}

Selectively publishing results that support the tested hypotheses (`positive' results) distorts the available evidence for scientific claims. For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature. A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known. We compared the results in published Registered Reports (N = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (N = 152) in Psychology. Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports. We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-1 error inflation in the Registered-Reports literature.
}

@@

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
But when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies\(\,\)---\(\,\)in the worst case it accumulates, leading us away from the truth rather than towards it.
Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.

@@

A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with \enquote{negative} results.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to more false positives; see Lakens, 2019).
These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2019).

@@

In a recent commentary, Allen and Mehler (2019) reported a similar investigation:
With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.

@@

In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
The coding procedure was identical for both article formats in all other respects.
Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
MS coded all papers in the sample, AS double-coded all papers MS had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's kappa = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We overturned the preregistered plan that AS would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).

@@

We expected a large proportion of Registered Reports to be replications, many of which may have been motivated by scepticism of the original study.
Because this circumstance alone could potentially lead to a lower positive result rate in Registered Reports, we additionally coded if hypotheses were close replications of previously published work.
Due to ill-specified coding criteria in our preregistration (see Appendix), we used an unregistered coding strategy:
We determined whether the coded hypothesis of papers whose full text contained the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019) was a close replication with the goal to verify a previously published result.
Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
AS coded all papers, DL double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
There were 5 disagreements (Cohen's kappa = .878), all were resolved by discussion.

@@

The positive result rate we found in standard reports (\(96.05 \%\)) is slightly but non-significantly higher than the \(91.5\%\) reported by Fanelli (2010).
Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf. Fanelli, 2012).
Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen and Mehler (2019), despite some differences in method and studied population.

@@

Since coders could not be blinded to an article's publication format, their judgment may have been biased.
Our study was not an experiment\(\,\)---\(\,\)hypotheses, authors, and editors were not randomly assigned to each publication format\(\,\)---\(\,\)and thus precludes strong causal inferences.
As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate.
Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds.
One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and type-I error inflation for all empirical articles they publish.
This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (\emph{Attention, Perception, and Psychophysics}, \emph{Cognition and Emotion}, and \emph{Frontiers in Psychology}) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
In these three journals, \(11/13\) (\(84.62\%\); \(95 \%\) CI {[}54.55, 98.08{]}) standard reports had positive results, compared to only \(7/14\) (\(50.00\%\); \(95 \%\) CI {[}23.04, 76.96{]}) Registered Reports.

@@

Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.
The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research.
Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered-Reports literature.
The absence of negative results is a serious threat to a cumulative science.
In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?}
The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature\(\,\)---\(\,\)and may be one solution to achieve a more credible scientific record.

@@

\href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.17; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.1.1; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.26; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.16; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 1.18; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).

@@

Conceptualisation: A.S. \& D.L.; data curation, formal analysis, and software: A.S. \& M.S.; investigation, methodology, and validation: A.S., M.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing\(\,\)---\(\,\)original draft: A.S; writing\(\,\)---\(\,\)review and editing: A.S., M.S., \& D.L.

@@

This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leonid Tiokhin, and Stuart Ritchie for valuable comments that helped improve this manuscript.

\hypertarget{prior-versions}{%
\subsubsection{Prior versions}\label{prior-versions}}

A preprint of this manuscript has been published on \emph{PsyArXiv} (\url{https://doi.org/10.31234/osf.io/p6e9c}). All sections of the present manuscript have been shortened to comply with the submission guidelines, but are intended to contain the same arguments, methods, results, and conclusions as the preprint.

@@

\leavevmode\hypertarget{ref-Lakens2019b}{}%
Lakens, D. (2019). The Value of Preregistration for Psychological Science: A Conceptual Analysis. \url{https://doi.org/10.31234/osf.io/jbh4w}

\leavevmode\hypertarget{ref-Lakens2018a}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. \url{https://doi.org/10.1016/j.ympev.2015.01.015}

@@

\leavevmode\hypertarget{ref-Makel2019}{}%
Makel, M. C., Hodges, J., Cook, B. G., \& Plucker, J. (2019). Questionable and Open Research Practices in Education Research. \url{https://doi.org/10.35542/osf.io/f7srb}

>>>>

% Manuscript styling
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{Positive Results in Standard vs Registered Reports}
\author{Anne M. Scheel\textsuperscript{1}, Mitchell R. M. J. Schijen\textsuperscript{1}, \& Daniël Lakens\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Eindhoven University of Technology}
\authornote{

@@

\abstract{
\vspace{0.4cm} \begin{tcolorbox}[colback=white,colframe=electricviolet,coltext=electricviolet,
   fontupper=\normalsize,borderline={0.3mm}{0.3mm}{white}]
 A copy-edited version of this manuscript is now published at \textsl{Advances in Methods and Practices in Psychological Science}. Please cite as:
  \vspace{0.2cm}
 \begin{center}
 Scheel, A. M., Schijen, M. R. M. J., \& Lakens, D. (2021). An excess of positive results: Comparing the standard Psychology literature with Registered Reports. \textsl{Advances in Methods and Practices in Psychological Science, 4}(2). \url{https://doi.org/10.1177/25152459211007467}
 \end{center}
\end{tcolorbox} \vspace{0.5cm}

Selectively publishing results that support the tested hypotheses (`positive' results) distorts the available evidence for scientific claims. For the past decade, psychological scientists have been increasingly concerned about the degree of such distortion in their literature. A new publication format has been developed to prevent selective reporting: In Registered Reports, peer review and the decision to publish take place before results are known. We compared the results in published Registered Reports (\emph{N} = 71 as of November 2018) with a random sample of hypothesis-testing studies from the standard literature (\emph{N} = 152) in Psychology. Analysing the first hypothesis of each paper, we found \(96\%\) positive results in standard reports, but only \(44\%\) positive results in Registered Reports. We discuss possible explanations for this large difference and suggest that a plausible factor is the reduction of publication bias and/or Type-I error inflation in the Registered-Reports literature.
}

@@

If the scientific literature were a faithful representation of the research scientists conduct, a cumulative science would be a powerful tool to infer what is true about the world.
When random error is the only threat to the accuracy of individual findings, aggregating across many findings allows inferences about the presence and size of effects with a certain reliability.
But when published findings are systematically biased, cumulative science breaks down:
Unlike random error, bias does not cancel out when aggregating across studies\(\,\)---\(\,\)in the worst case, it accumulates, leading us away from the truth rather than towards it.
Unfortunately, there is reason to believe that the Psychology literature is not a faithful representation of all research psychologists conduct.

@@

A more plausible explanation for these numbers may be a selection bias towards statistically significant results in the published literature.
We can distinguish two broad categories of bias: \enquote{publication bias} and \enquote{questionable research practices}.
Publication bias describes publishing behaviours that give manuscripts which find support for their tested hypotheses a higher chance of being published than manuscripts with \enquote{negative} results.
These include editors and reviewers selectively rejecting manuscripts with negative results (``reviewer bias'', Greenwald, 1975; Mahoney, 1977) and researchers deciding not to submit studies with negative results for publication (``file-drawering''; Rosenthal, 1979).
Questionable research practices (QRPs) describe research behaviours that make evidence in favour of a certain conclusion look stronger than it is (typically, though not always, leading to more false positives; see Lakens, 2019).
These include presenting unexpected results as having been predicted \emph{a priori} (HARKing, short for ``hypothesising after results are known''; Kerr, 1998) and exploiting flexibility in data analysis to obtain statistically significant results (``\emph{p}-hacking''; Simmons, Nelson, \& Simonsohn, 2011).
Evidence for both categories of bias exist:
Publication bias has been observed in peer review (Atkinson, Furlong, \& Wampold, 1982; Mahoney, 1977) and in longitudinal data from an NSF grant programme that found a file-drawering effect for studies with negative results (Franco, Malhotra, \& Simonovits, 2014, 2016); and QRPs have been admitted by scientists in several survey studies (Agnoli, Wicherts, Veldkamp, Albiero, \& Cubelli, 2017; Fiedler \& Schwarz, 2016; Fraser, Parker, Nakagawa, Barnett, \& Fidler, 2018; John, Loewenstein, \& Prelec, 2012; Makel, Hodges, Cook, \& Plucker, 2021).

@@

In a recent commentary, Allen \& Mehler (2019) reported a similar investigation:
With a self-developed coding method, they surveyed the 127 biomedical and Psychology Registered Reports listed in the COS database as of September 2018 and found \(60.5\%\) unsupported hypotheses across all included Registered Reports (counting all hypotheses in each paper).
A major advantage of our study, which was planned around the same time (we were unaware of Allen and Mehler's parallel efforts), is the ability to directly compare Registered Reports with the standard literature.
In addition, we replicate Fanelli (2010) and provide data to evaluate his method: The search term \enquote{test\(^\ast\) the hypothes\(^\ast\)} might introduce selection effects, meaning that results obtained this way may not generalise to hypothesis-testing studies that do not use this phrase.
To this end, we coded the phrases used to introduce hypotheses in Registered Reports, analysed how many of them would have been detected with Fanelli's search term, and compiled a list of alternative search terms to test the generalisability of Fanelli's results in the future.
Finally, we share a rich dataset containing the exact quotes of hypotheses and conclusions on which we based our judgements, as well as detailed descriptions of our sampling and coding procedure (see Appendix).
This allows others to verify (or contest) our results and can hopefully provide an interesting resource for future meta-scientific research.

@@

In Registered Reports, we coded the first \emph{preregistered} hypothesis, thus excluding unregistered pilot studies.
The coding procedure was identical for both article formats in all other respects.
Coding disagreements between \enquote{full} and \enquote{partial} support were deemed minor since they would not affect the final results.
Thus, only disagreements affecting the binary support (full or partial) vs no support classification were treated as major and resolved through discussion.
M.S. coded all papers in the sample, A.S. double-coded all papers M.S. had found difficult to code or could not code (\(24\) RRs and \(47\) SRs).
Only 3 disagreements were major (Cohen's \(\kappa\) = .808) and subsequently resolved by discussion; 15 were minor (disagreement between \enquote{support} and \enquote{partial support}).
We overturned the preregistered plan that A.S. would additionally code a random subset of both groups, because the number of double-coded papers seemed sufficient after double-coding only the difficult cases.
Because removing all indicators that could have identified Registered Reports as such from their full texts would have been practically impossible, coding was not blind to publication format (Registered Report vs standard report).

@@

We expected a large proportion of Registered Reports to be replications, many of which may have been motivated by scepticism of the original study.
Because this circumstance alone could potentially lead to a lower positive result rate in Registered Reports, we additionally coded if hypotheses were close replications of previously published work.
Due to ill-specified coding criteria in our preregistration (see Appendix), we used an unregistered coding strategy:
We determined whether the coded hypothesis of papers whose full text contained the string \enquote{replic\(^\ast\)} (cf. Makel, Plucker, \& Hegarty, 2012; Mueller-Langer, Fecher, Harhoff, \& Wagner, 2019) was a close replication with the goal to verify a previously published result.
Conceptual replications and internal replications (replication of a study in the same paper) were not counted as replications in this narrow sense, since both are more likely to be motivated by the goal to build on previous work than by scepticism.
A.S. coded all papers, D.L. double-coded 32 Registered Reports (\(45.07 \%\)) and 99 standard reports (\(65.13 \%\)).
There were 5 disagreements (Cohen's \(\kappa\) = .878), all were resolved by discussion.

@@

The positive result rate we found in standard reports (\(96.05 \%\)) is slightly but non-significantly higher than the \(91.5\%\) reported by Fanelli (2010).
Our replication in a more recent sample of the Psychology literature thus yielded a comparably high estimate of supported hypotheses, but we cannot rule out that the positive result rate in the population has increased since 2010 (cf. Fanelli, 2012).
Furthermore, our estimate of the positive result rate for Registered Reports (\(43.66 \%\)) is comparable to the \(39.5\%\) reported by Allen \& Mehler (2019), despite some differences in method and studied population.

@@

Since coders could not be blinded to an article's publication format, their judgment may have been biased.
Our study was not an experiment\(\,\)---\(\,\)hypotheses, authors, and editors were not randomly assigned to each publication format\(\,\)---\(\,\)and thus precludes strong causal inferences.
As discussed above, it seems highly plausible that Registered Reports reduce publication bias and QRPs, which in turn reduces the positive result rate.
Yet we neither know exactly how effective Registered Reports are at reducing bias, nor how large the effect on positive results would be in the absence of potential confounds.
One such confound, as just discussed, could be that Registered Reports may be used for particularly risky hypotheses.
Another confound could be that the format attracts particularly conscientious authors who try to minimise the risk of inflated error rates regardless of the report format they use.
As a third potential confound, journals that offer Registered Reports may have more progressive editorial policies which aim to reduce publication bias and Type-I error inflation for all empirical articles they publish.
This could lead to less bias in the Registered-Reports literature even if the format's safeguards against certain QRPs were actually ineffective.
Additional research, ideally with prospective and experimental or quasi-experimental study designs, is needed to further investigate the influence of such factors.
However, a cursory look at the three journals which contributed both standard reports and Registered Reports to our dataset (\emph{Attention, Perception, and Psychophysics}; \emph{Cognition and Emotion}; and \emph{Frontiers in Psychology}) suggests that the pattern observed in our main analysis may hold for within-journal comparisons, which would speak against a strong influence of an editorial-policy confound:
In these three journals, \(11/13\) (\(84.62\%\); \(95 \%\) CI {[}54.55, 98.08{]}) standard reports had positive results, compared to only \(7/14\) (\(50.00\%\); \(95 \%\) CI {[}23.04, 76.96{]}) Registered Reports.

@@

Our study presents a systematic comparison of positive results in Registered Reports and the standard literature.
The much lower positive result rate in Registered Reports compared to standard reports suggests that an unbiased literature would look very different from the existing body of published research.
Standard publication formats seem to lead psychological scientists to miss out on many negative results from high-quality studies, which are available in the Registered-Reports literature.
The absence of negative results is a serious threat to a cumulative science.
In 1959, Sterling asked: \enquote{What credence can then be given to inferences drawn from statistical tests of \(H_0\) if the reader is not aware of all experimental outcomes of a kind?} (p.~33).
The amount of experimental outcomes missing from the standard literature appears to be so large that not much credence may be left.
In contrast, Registered Reports have clearly led to a much larger proportion of negative results appearing in the literature\(\,\)---\(\,\)and may be one solution to achieve a more credible scientific record.

@@

\href{https://osf.io/aqr2s/}{Data} and code necessary to reproduce all analyses reported here, as well as the \href{https://osf.io/qw798/}{Appendix}, the \href{https://osf.io/sy927/}{preregistration}, and additional supplementary files, are available at \url{https://osf.io/dbhgr}.
The manuscript, including figures and statistical analyses, the \href{https://osf.io/qw798/}{Appendix}, and the \href{https://osf.io/6jrkz/}{codebook} available in the supplement were created using RStudio (1.2.5019, RStudio Team, 2019) and R (Version 3.6.0; R Core Team, 2019) and the R-packages \emph{bookdown} (Version 0.24; Xie, 2016), \emph{codebook} (Version 0.8.2; Arslan, 2018), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{knitr} (Version 1.34; Xie, 2015), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{reshape2} (Version 1.4.3; Wickham, 2007), \emph{rio} (Version 0.5.27; Chan, Chan, Leeper, \& Becker, 2018), \emph{rmarkdown} (Version 2.10; Xie, Allaire, \& Grolemund, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tidyr} (Version 1.0.0; Wickham \& Henry, 2019), and \emph{TOSTER} (Version 0.3.4; Lakens, 2017).

@@

Conceptualisation: A.S. \& D.L.; data curation, formal analysis, and software: A.S. \& M.R.M.J.S.; investigation, methodology, and validation: A.S., M.R.M.J.S., \& D.L; supervision: A.S \& D.L.; visualisation and writing\(\,\)---\(\,\)original draft: A.S; writing\(\,\)---\(\,\)review and editing: A.S., M.R.M.J.S., \& D.L.

@@

This work was funded by VIDI grant 452-17-013. We thank Chris Chambers, Emma Henderson, Leo Tiokhin, Stuart Ritchie, and Simine Vazire for valuable comments that helped improve this manuscript.

@@

\leavevmode\hypertarget{ref-Lakens2019}{}%
Lakens, D. (2019). The value of preregistration for psychological science: A conceptual analysis. \emph{Japanese Psychological Review}, \emph{62}(3), 221--230. \url{https://doi.org/10.24602/sjpr.62.3_221}

\leavevmode\hypertarget{ref-Lakens2018a}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. \url{https://doi.org/10.1177/2515245918770963}

@@

\leavevmode\hypertarget{ref-Makel2021}{}%
Makel, M. C., Hodges, J., Cook, B. G., \& Plucker, J. A. (2021). Both Questionable and Open Research Practices Are Prevalent in Education Research: \emph{Educational Researcher}. \url{https://doi.org/10.3102/0013189X211001356}

\leavevmode\hypertarget{ref-Agnoli2017}{}%
Agnoli, F., Wicherts, J. M., Veldkamp, C. L. S., Albiero, P., \& Cubelli, R. (2017). Questionable research practices among italian research psychologists. \emph{PLOS ONE}, \emph{12}(3), e0172792. \url{https://doi.org/10.1371/journal.pone.0172792}

\leavevmode\hypertarget{ref-Lakens2019}{}%
Lakens, D. (2019). The value of preregistration for psychological science: A conceptual analysis. \emph{Japanese Psychological Review}, \emph{62}(3), 221--230. \url{https://doi.org/10.24602/sjpr.62.3_221}

\leavevmode\hypertarget{ref-Lakens2018a}{}%
Lakens, D., Scheel, A. M., \& Isager, P. M. (2018). Equivalence Testing for Psychological Research: A Tutorial. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(2), 259--269. \url{https://doi.org/10.1177/2515245918770963}

\leavevmode\hypertarget{ref-Makel2021}{}%
Makel, M. C., Hodges, J., Cook, B. G., \& Plucker, J. A. (2021). Both Questionable and Open Research Practices Are Prevalent in Education Research: \emph{Educational Researcher}. \url{https://doi.org/10.3102/0013189X211001356}
